Linear instability underlying synchronous waving of marine grass in flow

### 2014-09-05 Paper/grass.tex
Moved comparison with terrestrial to discussion

Similar phenomenon of large amplitude coherent oscillation of canopy in atmospheric flow known as ho-nami\cite{Inoue56,Raupach96}, have also been observed.
A crucial difference between the atmospheric and aquatic flow is that the atmospheric flows are essentially unbounded vertically\cite{Vivoni98,Nepf00}. 
Another major difference between the two is the considerable difference of stiffness of canopies; terrestrial canopies tend to be much more rigid, whereas aquatic canopies are buoyant\cite{Vivoni98,Ghisal02}.
Due to these differences between aquatic and marine flow, our analysis of flow in presence of vegetation in a bounded domain is applicable only to marine canopies.

@@

>>>>

@@

Similar phenomenon of large amplitude coherent oscillation of terrestrial canopies in atmospheric flow known as ho-nami\cite{Inoue56,Raupach96}, have also been observed.
A crucial difference between the atmospheric and aquatic flow is that the atmospheric flows are essentially unbounded vertically\cite{Vivoni98,Nepf00}. 
Another major difference between the two is the considerable difference of stiffness of canopies; terrestrial canopies tend to be much more rigid, whereas aquatic canopies are buoyant\cite{Vivoni98,Ghisal02}.
Due to these differences between aquatic and marine flow, our analysis of flow in presence of vegetation in a bounded domain is applicable only to marine canopies.
